Evaluation of Diagnostic Concordance Between Algorithms for Parkinson’s Disease Dementia

### 2025-10-09 _manuscript/manuscript.qmd
The first build of the package.

upstore <- here::here(tar_config_get("store"))
tar_source(here::here("R"))
data <- tar_read(raw_data, store = upstore)
crit <- tar_read(pdd_data, store = upstore)$criteria
vars <- tar_read(variables, store = upstore)
```

@@

desc <- tar_read(sample_description, store = upstore)
rates <- tar_read(rate_summaries, store = upstore)
algos <- tar_read(algorithms, store = upstore)
pred <- tar_read(demographic_predictors, store = upstore)
conc <- tar_read(concordance_statistics, store = upstore)
kappa <- tar_read(kappa_summmaries, store = upstore)
perc <- rates$table$perc

>>>>

upstore <- here::here(tar_config_get("store"))
tar_source(here::here("R"))

load_target <- function(x) {
  tar_read_raw(x, store = upstore)
}

data <- load_target("raw_data")
crit <- load_target("pdd_data")$criteria
vars <- load_target("variables")
```

@@

desc  <- load_target("sample_description")
rates <- load_target("rate_summaries")
algos <- load_target("algorithms")
pred  <- load_target("demographic_predictors")
conc  <- load_target("concordance_statistics")
kappa <- load_target("kappa_summmaries")
perc  <- rates$table$perc
